---
title: "Activity 2.1 - Exploratory Data Analysis: Summarizing and Manipulating"
author: Purple Group (Section 01)
date: 9/3/2019
output: 
  html_document: 
    keep_md: yes
---

### Load packages

```{r other, message=FALSE}
library(tidyverse) 
```

### Load data

```{r load-data, message=FALSE}
college_recent_grads <- read_csv("data/recent-grads.csv") 

college_recent_grads %>%
  arrange(unemployment_rate) %>%
  select(rank, major, unemployment_rate) %>%
  mutate(unemployment_rate = round(unemployment_rate, digits = 4))
options(digits = 2)





```


### Exercise One

Altering the number of digits displayed without touching the input data is the better option because it organizes the data set while still maintaining the set in it's entirity.

### Exercise 2

Zoology (.637), Visual And Performing Arts (.746), United States History (.430).
```{r}
college_recent_grads %>%
  arrange(desc(major)) %>%
  select(rank, major, sharewomen)%>%
head(3)
```


### Exercise 3

The median is used for such data because the median is a robust statistic and is not succeptible to outliers like the mean is.

```{r}
college_recent_grads %>%
  arrange(unemployment_rate) %>%
  select(rank, major, unemployment_rate) %>%
  mutate(unemployment_rate = round(unemployment_rate, digits = 4))
  
  college_recent_grads %>%
  arrange(desc(unemployment_rate)) %>%
  select(rank, major, unemployment_rate)
```



### Exercise 4
We chose a binwidth of 5000 because the minimum median salary is $22000 and 1000 seemed too low.
...

### Exercise 5
The distribution is right skewed with one extreme outlier, I would suggest using the median as a measure of central tendency. (Median salary = $36,000)
```{r}
ggplot(data = college_recent_grads, mapping = aes(x = median)) +
  geom_histogram()
geom_histogram(binwidth = 5000)
```

...

### Exercise 6
```{r}
ggplot(data = college_recent_grads, mapping = aes(x = median)) +
  geom_histogram() +
  facet_wrap( ~ major_category, ncol = 4)
geom_histogram(binwidth = 5000)
```

...

### Exercise 7
Engineering has the highest median salary.
```{r}
college_recent_grads %>%
  group_by(major_category) %>%
  summarise(med = median(median)) %>%
  arrange(desc(med))
```

...

### Exercise 8
The least popular is Interdisciplinary with count (n = 1)
```{r}
college_recent_grads %>%
  count(major_category) %>%
 arrange(n)
```

...


### Exercise 9
STEM majors with median salaries less than or equal to the median for all majors' median earnings are Environmental Science, Multi-Disciplinary Or General Science, Physiology, Communication Technologies, Neuroscience, Atmospheric Sciences And Meteorology, Miscellaneous Biology, Biology, Ecology, and Zoology.

```{r}
stem_categories <- c("Biology & Life Science",
                     "Computers & Mathematics",
                     "Engineering",
                     "Physical Sciences")

college_recent_grads <- college_recent_grads %>%
  mutate(major_type = ifelse(major_category %in% stem_categories, "stem", "not stem"))

college_recent_grads %>%
  filter(
    major_type == "stem",
    median < 36000
  )%>%
arrange(desc(median))%>%
select(major, median, p25th, p75th)
```

...

### Exercise 10
The trend of the data suggests that the proportion of women in STEM fields is lower than the proportion of women in non-STEM fields, but the women in STEM fields tend to have higher median salaries respectively in comparison to women in non-STEM fields. 
```{r}
ggplot(data = college_recent_grads, mapping = aes(x = sharewomen, y = median, color = major_type)) +
  geom_point()
```

...
