---
title: "Activity 2.1 - Exploratory Data Analysis: Summarizing and Manipulating"
author: Purple Group (Section 01)
date: 9/3/2019
output: 
  html_document: 
    keep_md: yes
---

### Load packages

```{r other, message=FALSE}
library(tidyverse) 
```

### Load data

```{r load-data, message=FALSE}
college_recent_grads <- read_csv("data/recent-grads.csv") 

```


### Exercise 1

Altering the number of digits displayed without touching the input data is the better option because it organizes the data set while still maintaining the set in its entirety.

### Exercise 2

```{r unemployment-by-sharewomen}
options(digits = 2)

college_recent_grads %>%
  arrange(desc(unemployment_rate)) %>%
  select(rank, major, unemployment_rate) %>%
  ##mutate(unemployment_rate = round(unemployment_rate, digits = 4))
  head(3)

college_recent_grads %>%
  arrange(desc(sharewomen)) %>%
  select(major, total, sharewomen,) %>%
  head(3)
```

The majors with highest unemployment rates with the greatest proportions of women are Early Childhood Education, Communication Disorders Sciences And Services, and Medical Assisting Services.

### Exercise 3

The median is used for such data because the median is a robust statistic and is not succeptible to outliers like the mean is.


### Exercise 4
We chose a binwidth of 5000 because the minimum median salary is $22000 and 1000 seemed too low.

```{r median-salaries}
ggplot(data = college_recent_grads, mapping = aes(x = median)) +
  geom_histogram(binwidth = 5000)
```


### Exercise 5

```{r summary-stats}
college_recent_grads %>%
  summarise(min = min(median), 
            max = max(median),
            mean = mean(median),
            med = median(median),
            sd = sd(median), 
            q1 = quantile(median, probs = 0.25),
            q3 = quantile(median, probs = 0.75))
```

The distribution is right skewed with one extreme outlier, we would suggest using the median as a measure of central tendency. (Median salary = $36,000)

### Exercise 6

```{r median-salary-by-major_category}
ggplot(data = college_recent_grads, mapping = aes(x = median)) +
  geom_histogram() +
  facet_wrap( ~ major_category, ncol = 4)
geom_histogram(binwidth = 5000)
```


### Exercise 7
Engineering has the highest median salary.

```{r highest-median-salary}
college_recent_grads %>%
  group_by(major_category) %>%
  summarise(med = median(median)) %>%
  arrange(desc(med))
```


### Exercise 8
The least popular is Interdisciplinary with count (n = 1)

```{r least-popular-major-in-dataset}
college_recent_grads %>%
  count(major_category) %>%
 arrange(n)
```


### Exercise 9
STEM majors with median salaries less than or equal to the median for all majors' median earnings are Environmental Science, Multi-Disciplinary Or General Science, Physiology, Communication Technologies, Neuroscience, Atmospheric Sciences And Meteorology, Miscellaneous Biology, Biology, Ecology, and Zoology.

```{r stem-salaries}
stem_categories <- c("Biology & Life Science",
                     "Computers & Mathematics",
                     "Engineering",
                     "Physical Sciences")

college_recent_grads <- college_recent_grads %>%
  mutate(major_type = ifelse(major_category %in% stem_categories, "stem", "not stem"))

college_recent_grads %>%
  filter(
    major_type == "stem",
    median < 36000
  )%>%
arrange(desc(median))%>%
select(major, median, p25th, p75th)
```


### Exercise 10
The trend of the data suggests that the proportion of women in STEM fields is lower than the proportion of women in non-STEM fields, but the women in STEM fields tend to have higher median salaries respectively in comparison to women in non-STEM fields. 

```{r women-in-stem-vs-nonstem}
ggplot(data = college_recent_grads, mapping = aes(x = sharewomen, y = median, color = major_type)) +
  geom_point()
```


