---
title: "Activity 2.1 - Exploratory Data Analysis: Summarizing and Manipulating"
author: other
date: 9/3/2019
output: 
  html_document: 
    keep_md: yes
---

### Load packages

```{r other, message=FALSE}
library(tidyverse) 
```

### Load data

```{r load-data, message=FALSE}
college_recent_grads <- read_csv("data/recent-grads.csv") 

college_recent_grads %>%
  arrange(unemployment_rate) %>%
  select(rank, major, unemployment_rate) %>%
  mutate(unemployment_rate = round(unemployment_rate, digits = 4))
options(digits = 2)

college_recent_grads %>%
  arrange(desc(major)) %>%
  select(rank, major, sharewomen)%>%
head(3)


```


### Exercise One

Altering the number of digits displayed without touching the input data is the better option because it organizes the data set while still maintaining the set in it's entirity.

### Exercise 2

Zoology (), Visual And Performing Arts (), United States History ().

### Exercise 3

The median is used for such data because the median is a robust statistic and is not succeptible to outliers like the mean is.


### Exercise 4

...

### Exercise 5

...

### Exercise 6

...

### Exercise 7

...

### Exercise 8

...

### Exercise 9

...

### Exercise 10

...
