---
title: "Activity 2.1 - Exploratory Data Analysis: Summarizing and Manipulating"
author: other
date: 9/3/2019
output: 
  html_document: 
    keep_md: yes
---

### Load packages

```{r other, message=FALSE}
library(tidyverse) 
```

### Load data

```{r load-data, message=FALSE}
college_recent_grads <- read_csv("data/recent-grads.csv") 

college_recent_grads %>%
  arrange(unemployment_rate) %>%
  select(rank, major, unemployment_rate) %>%
  mutate(unemployment_rate = round(unemployment_rate, digits = 4))
options(digits = 2)

college_recent_grads %>%
  arrange(desc(major)) %>%
  select(rank, major, sharewomen)%>%
head(3)

ggplot(data = college_recent_grads, mapping = aes(x = median)) +
  geom_histogram()
geom_histogram(binwidth = 5000)

college_recent_grads %>%
  summarise(min = min(median), 
            max = max(median),
            mean = mean(median),
            med = median(median),
            sd = sd(median), 
            q1 = quantile(median, probs = 0.25),
            q3 = quantile(median, probs = 0.75))

ggplot(data = college_recent_grads, mapping = aes(x = median)) +
  geom_histogram() +
  facet_wrap( ~ major_category, ncol = 4)
geom_histogram(binwidth = 5000)

college_recent_grads %>%
  group_by(major_category) %>%
  summarise(med = median(median)) %>%
  arrange(desc(med))

college_recent_grads %>%
  count(major_category) %>%
 arrange(desc(n))

stem_categories <- c("Biology & Life Science",
                     "Computers & Mathematics",
                     "Engineering",
                     "Physical Sciences")

college_recent_grads <- college_recent_grads %>%
  mutate(major_type = ifelse(major_category %in% stem_categories, "stem", "not stem"))

college_recent_grads %>%
  filter(
    major_type == "stem",
    median < 36000
  )%>%
arrange(desc(median))%>%
select(major, median, p25th, p75th)
```


### Exercise One

Altering the number of digits displayed without touching the input data is the better option because it organizes the data set while still maintaining the set in it's entirity.

### Exercise 2

Zoology (.637), Visual And Performing Arts (.746), United States History (.430).

### Exercise 3

The median is used for such data because the median is a robust statistic and is not succeptible to outliers like the mean is.


### Exercise 4
We chose a binwidth of 5000 because the minimum median salary is $22000 and 1000 seemed too low.
...

### Exercise 5
The distribution is right skewed with one extreme outlier, I would suggest using the median as a measure of central tendency. (Median salary = $36,000)
...

### Exercise 6
```
ggplot(data = college_recent_grads, mapping = aes(x = median)) +
  geom_histogram() +
  facet_wrap( ~ major_category, ncol = 4)
geom_histogram(binwidth = 5000)

(See above for actual distributions)
```
...

### Exercise 7
Engineering has the highest median salary.
...

### Exercise 8
The least popular is Interdisciplinary with count (n = 1)
...

### Exercise 9

...

### Exercise 10

...
